---
title: "Test calling clonal cnvs in ST1R-Nuc"
output:
  html_document:
    df_print: paged
---
Here, we look at the results of running scAbsolute on this sample.


```{r}
library(ComplexHeatmap)
library(data.table)
library(QDNAseq)
library(RColorBrewer)
library(HMMcopy)
library(doParallel)
library(gtools)
library(ggplot2)


source("~/scAbsolute-main/R/visualization.R")
source("~/scAbsolute-main/R/mean-variance.R")
source("~/scAbsolute-main/R/scAbsolute.R")
source("~/scAbsolute-main/R/core.R")



source("~/MB_SCSEQ/Figure01/CloneInference/commonSegmentation.R")
source("~/MB_SCSEQ/Figure01/CloneInference/plotFunctionsCNV.R")
source("~/MB_SCSEQ/Figure01/CloneInference/inferClonalCNVProfiles.R")
source("~/MB_SCSEQ/Figure01/CloneInference/calculateBootstrappedStatistics.R")
```

## 10x data

Load in the results for all the STP samples here:

```{r}


ST1R <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPR-Nuclei/500/predict/out.rds")
protocolData(ST1R) <- AnnotatedDataFrame()
colnames(ST1R) <- gsub(colnames(ST1R), pat = "\\-[0-9]\\.filtered\\.sorted$", rep = "")

# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPR-Nuclei//500/predict/out.rds")

# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/RCMB18-PDX/500/predict/out.rds")


# STPPDXres <- STPPDXres[,STPPDXres$ploidy.mod %in% seq(1,4)]
# STPRPDXres <- STPRPDXres[,STPRPDXres$ploidy.mod %in% seq(1,4)]
# ST1R <- ST1R[,ST1R$ploidy.mod %in% seq(1,4)]
# STPRNucres <- STPRNucres[,STPRNucres$ploidy.mod %in% seq(1,4)]

```

## ST1R clone identification

```{r}


hist(ST1R$observed.variance/ST1R$expected.variance, breaks = 50)
abline(v=mad(ST1R$observed.variance/ST1R$expected.variance)*2+median(ST1R$observed.variance/ST1R$expected.variance))
```

There are clear outliers based on variance, which we remove.

```{r}

hist(ST1R$gini_normalized, breaks = 50)
abline(v=mad(ST1R$gini_normalized)*2+median(ST1R$gini_normalized))

```

```{r}

hist(ST1R$error, breaks = 60)
abline(v=mad(ST1R$error)*2+median(ST1R$error))

```


```{r}

var.filter <- mad(ST1R$observed.variance/ST1R$expected.variance)*2+median(ST1R$observed.variance/ST1R$expected.variance) > ST1R$observed.variance/ST1R$expected.variance
gini.filter <- mad(ST1R$gini_normalized)*2+median(ST1R$gini_normalized) > ST1R$gini_normalized
# error.filter <- mad(ST1R$error)*2+median(ST1R$error) > ST1R$error
## Ploidy 0 doesn't work for ploidy normalization
ploidy.filter <- ST1R$ploidy.mod > 0
ST1R <- ST1R[,var.filter&gini.filter&ploidy.filter]

```


Lets plot all the cell results for manual review:

```{r}

plotDataset(ST1R, file="ST1R_Nuc_scAbs_allcells.pdf", f=plotCopynumber)

```


```{r}
ST1RSegmented <- mapCellsToCommonBreakpoints(ST1R, mergeWidth = 2)

ploidy.data <- data.frame(chr="ploidy", "start"=-1, end=-1)
ploidy.data <- cbind(ploidy.data, t(data.frame(ST1R$ploidy.mod)))

ST1R.ploidy.normed <- copy(ST1RSegmented)

for(cell in colnames(ST1R)){
  
  ST1R.ploidy.normed[,(cell):= ST1R.ploidy.normed[,cell, with=F]/ ST1R[,cell]$ploidy.mod*2]
}

ST1R.ploidy.normed <- rbind(ST1R.ploidy.normed, ploidy.data, use.names=F)


```

```{r}
dendroOrder <- rowSums(abs(t(assayDataElement(ST1R, "copynumber"))-ST1R$ploidy.mod), na.rm = TRUE)

annot_rows = rowAnnotation(ploidy=ST1R$ploidy.mod, "obs/exp var"=ST1R$observed.variance/ST1R$expected.variance, "gini"=ST1R$gini, error=ST1R$error)


ploidy.normed.man.wardd2 <- hclust(dist(t(ST1R.ploidy.normed[,c(-1,-2,-3)]), method="manhattan"), method = "ward.D2")

  
plotComplexHeatmapCommonSegs(ST1RSegmented, clust.rows=ploidy.normed.man.wardd2, annot_rows=annot_rows)
  
```

```{r}

annot_rows = rowAnnotation(ploidy=ST1R$ploidy.mod, "obs/exp var"=ST1R$observed.variance/ST1R$expected.variance, "gini"=ST1R$gini, error=ST1R$error)


bins.man.wardd2 <- clusterMannhattanOnBins(ST1R)

denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),dendroOrder)


# xx <- prcomp(t(ST1RSegmented[complete.cases(ST1RSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(ST1RSegmented, clust.rows=denrToPlot, annot_rows=annot_rows)#, column_title = unique(featureData(ST1R)$chromosome))
  
```

```{r}

annot_rows = rowAnnotation(ploidy=ST1R$ploidy.mod, "obs/exp var"=ST1R$observed.variance/ST1R$expected.variance, "gini"=ST1R$gini, error=ST1R$error)


bins.cor.wardd2 <- clusterCorOnBins(ST1R)

denrToPlot <- reorder(as.dendrogram(bins.cor.wardd2),dendroOrder)


# xx <- prcomp(t(ST1RSegmented[complete.cases(ST1RSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(ST1RSegmented, clust.rows=denrToPlot, annot_rows=annot_rows)
  
```


```{r}
set.seed(42)# set the seed of random number generator 

list.of.packages <- c("HMMcopy", "doParallel", "gtools", "ggplot2")


# ignore all "simple" diagnostic messages (warnings or errors)
suppressMessages(invisible(lapply(list.of.packages, require, character.only = TRUE)))


window_length <- 5e7
min_cnv_changes <- 10

nBootSamples <- 50
min_consec_cnvs <- 5

nthread <- 10
registerDoParallel(nthread)

```


##                       READ IN DATA OF INTEREST
############################################################################
```{r, warning=FALSE, message=FALSE}
## set sample of interest
sample = 'ST1R-Nuclei'



## bin size param
bin_kb = 20
bin = bin_kb*1000





# get the readcounts for the bin size of interest
path_cells <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                     sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
path_to_readcounts <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                             sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
files <- list.files(path_to_readcounts, pattern = '.seg', full.names = F)

# set the paths to the reference files
gfile = paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.gc.seg')
mfile =  paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.map.seg')



## Make list of cells
cellList <- list()

names(files) <- sapply(strsplit(files, split = "_|-"), `[[`, 3)

cellList <- foreach(cell = colnames(ST1R)) %dopar% {
  print(paste0("Processing cell: ", cell))
  
  
  rfile <- paste(path_cells,files[[cell]],sep = "")
  cellData <- wigsToRangedData(rfile, gfile, mfile)
  
  correctReadcount2(cellData)

}
names(cellList) <- colnames(ST1R)



```


```{r}
library(doParallel)
registerDoParallel(10)

# clonal.cnv.res.boot <- inferClonalCNVs(ST1R, cellList, bootstrap = TRUE, nBoot=101)
# saveRDS(clonal.cnv.res.boot, file="st1r_nuc_boot_res.rds")
clonal.cnv.res.boot<-readRDS("st1r_nuc_boot_res.rds")
```


```{r}
for(ploidy in names(clonal.cnv.res.boot)){
  
  for(k in 1:12){
    pdf(paste0("ST1R_",ploidy,"_k_", k, "clones_psuedobulk.pdf"), height = 11, width = 8.5)
    print(plotClonalProfilesAtK(clonal.cnv.res.boot[ploidy], k))
    dev.off()
  }
  
}



```



Lets plot some GOF metrics for the different k selections:

```{r}


clusterGOFmetrics <- computeGOFMetrics(clonal.cnv.res.boot)

#First ploidy 2:

ploidy2GOF <- sapply(clusterGOFmetrics$Ploidy_2, `[[`, 1)


pdf("ST1R_Nuc_ploidy2GOFbyK.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()



```


```{r}

ploidy2.fstat <- sapply(clonal.cnv.res.boot$Ploidy_2, returnBootstrapFStats)
ploidy2.fstat
```


The F-Stat is suggesting that we actually have a lot of small outliers to remove. 

Lets try to UMAP/t-SNE this to take a look at the data. 


```{r}
library(uwot)
library(ggplot2)

my.umap <- umap(dist(t(ST1RSegmented[,-c(1:3), with=F])[ST1R$ploidy.mod==2,]))

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_2$k_6, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```


```{r}

my.mds <- cmdscale(dist(t(ST1RSegmented[,-c(1:3), with=F])[ST1R$ploidy.mod==2,]))


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```

```{r}
cluster_assignemntk2 <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_2$k_2, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignemntk2$Cluster[match(rownames(my.mds), cluster_assignemntk2$cells)])
ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```

Here, the f-stat seems to insist that k=6 is a better solution than k=2, but the UMAP doesn't 
really support that, (even when its tuned to small neighbourhoods,not shown)
The MDS makes it look more reasonable, explaining at least why removing some of the points improves
the F stat.



According the the f-stat, we select k=6 for the ploidy 2 state. 
The other states have too few cells to form a clone. 


 
```{r}

clonalCNVProfiles <- clonal.cnv.res.boot$Ploidy_2$k_1$Cluster_1$pseudobulk[,c(1,2,3), with=FALSE]

ploidy2clones <- lapply(clonal.cnv.res.boot$Ploidy_2$k_6, function(k.res){
  return(round(2^(k.res$hmmres$mus[,1]+1)[k.res$hmmres$state]))
})

ploidy2clones <- do.call(cbind,ploidy2clones[as.logical(sapply(ploidy2clones, length))])
  
clonalCNVProfiles <- cbind(clonalCNVProfiles,ploidy2clones)

colnames(clonalCNVProfiles)[-c(1:3)] <- paste0("Clone_", 1:2) 

```



```{r}

saveRDS(clonalCNVProfiles, file="~/ST1R_draft_clonal_cnv.rds")
png("~/ST1R_clonal_cnv_draft.png", width=10, height=5, unit="in", res=1000)
print(plotComplexHeatmapCommonSegs(clonalCNVProfiles, clust.rows = FALSE, column_title = unique(clonalCNVProfiles$chr)))
dev.off()
```


```{r}


ploidy2clonesCells <- lapply(clonal.cnv.res.boot$Ploidy_2$k_6, function(x) return(x['cells']))

ploidy2clonesCells <- ploidy2clonesCells[sapply(ploidy2clonesCells, function(x) length(x[[1]]))>=5]

allCloneCells <- ploidy2clonesCells

names(allCloneCells) <- paste0("Clone_", 1:2) 



cloneAssignment <- rbindlist(allCloneCells, idcol = "Clone")

if(any(!colnames(ST1R)%in%cloneAssignment$cells)){
  notAssignedCells <- data.frame(Clone = "Not Assigned", cells=colnames(ST1R)[!colnames(ST1R)%in%cloneAssignment$cells])
  cloneAssignment <- rbind(cloneAssignment, notAssignedCells)
}



write.csv(cloneAssignment, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/ST1R_Nuc_cell_clone_assignments.csv")

```

```{r}

HMMCopyMat <- sapply(cellList, `[[`, "copy")

HMMCopyMat <- cbind(cellList[[1]][,c(1:3)], HMMCopyMat)

write.csv(HMMCopyMat, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/ST1R_hmmcopy_20kb_logR.csv")


```


```{r}
library(dplyr)

gccor <- estimate_gc_correction(ST1R)

scAbsoluteRC <- assayDataElement(ST1R,"calls")*1/gccor

write.csv(scAbsoluteRC, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/ST1R_Nuclei_scAbsolute_500kb_corReadCount.csv")

scAbsoluteTCN <- assayDataElement(ST1R,"copynumber")
write.csv(scAbsoluteTCN, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/ST1R_Nuc_hmmcopy_500kb_TCN.csv")

```

