---
title: "Test calling clonal cnvs in MB243"
output:
  html_document:
    df_print: paged
---
Here, we look at the results of running scAbsolute on this sample.


```{r}
library(ComplexHeatmap)
library(data.table)
library(QDNAseq)
library(RColorBrewer)
library(HMMcopy)
library(doParallel)
library(gtools)
library(ggplot2)
library(GenomicRanges)


source("~/scAbsolute-main/R/visualization.R")
source("~/scAbsolute-main/R/mean-variance.R")
source("~/scAbsolute-main/R/scAbsolute.R")
source("~/scAbsolute-main/R/core.R")



source("~/MB_SCSEQ/Figure01/CloneInference/commonSegmentation.R")
source("~/MB_SCSEQ/Figure01/CloneInference/plotFunctionsCNV.R")
source("~/MB_SCSEQ/Figure01/CloneInference/inferClonalCNVProfiles.R")
source("~/MB_SCSEQ/Figure01/CloneInference/calculateBootstrappedStatistics.R")
```

## 10x data


```{r}


MB243 <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/MB243-Nuclei/500/predict/out.rds")
protocolData(MB243) <- AnnotatedDataFrame()
colnames(MB243) <- gsub(colnames(MB243), pat = "\\-[0-9]\\.filtered\\.sorted$", rep = "")

```

## MB243 clone identification

```{r}


hist(MB243$observed.variance/MB243$expected.variance, breaks = 50)
abline(v=mad(MB243$observed.variance/MB243$expected.variance)*2+median(MB243$observed.variance/MB243$expected.variance))
```

There are clear outliers based on variance, which we remove.

```{r}

hist(MB243$gini_normalized, breaks = 50)
abline(v=mad(MB243$gini_normalized)*2+median(MB243$gini_normalized))

```

```{r}

hist(MB243$error, breaks = 60)
abline(v=mad(MB243$error)*2+median(MB243$error))

```


```{r}

var.filter <- mad(MB243$observed.variance/MB243$expected.variance)*2+median(MB243$observed.variance/MB243$expected.variance) > MB243$observed.variance/MB243$expected.variance
gini.filter <- mad(MB243$gini_normalized)*2+median(MB243$gini_normalized) > MB243$gini_normalized
# error.filter <- mad(MB243$error)*2+median(MB243$error) > MB243$error
## Ploidy 0 doesn't work for ploidy normalization
ploidy.filter <- MB243$ploidy.mod > 0
MB243 <- MB243[,var.filter&gini.filter&ploidy.filter]

```


Lets plot all the cell results for manual review:

```{r, results='hide'}

plotDataset(MB243, file="MB243_scAbs_allcells.pdf", f=plotCopynumber, correction=TRUE)

```


```{r}
MB243Segmented <- mapCellsToCommonBreakpoints(MB243, mergeWidth = 2)

ploidy.data <- data.frame(chr="ploidy", "start"=-1, end=-1)
ploidy.data <- cbind(ploidy.data, t(data.frame(MB243$ploidy.mod)))

MB243.ploidy.normed <- copy(MB243Segmented)

for(cell in colnames(MB243)){
  
  MB243.ploidy.normed[,(cell):= MB243.ploidy.normed[,cell, with=F]/ MB243[,cell]$ploidy.mod*2]
}

MB243.ploidy.normed <- rbind(MB243.ploidy.normed, ploidy.data, use.names=F)


```

```{r}
dendroOrder <- rowSums(abs(t(assayDataElement(MB243, "copynumber"))-MB243$ploidy.mod), na.rm = TRUE)

annot_rows = rowAnnotation(ploidy=MB243$ploidy.mod, "obs/exp var"=MB243$observed.variance/MB243$expected.variance, "gini"=MB243$gini, error=MB243$error)


ploidy.normed.man.wardd2 <- hclust(dist(t(MB243.ploidy.normed[,c(-1,-2,-3)]), method="manhattan"), method = "ward.D2")

  
plotComplexHeatmapCommonSegs(MB243Segmented, clust.rows=ploidy.normed.man.wardd2, annot_rows=annot_rows)
  
```

```{r}

annot_rows = rowAnnotation(ploidy=MB243$ploidy.mod, "obs/exp var"=MB243$observed.variance/MB243$expected.variance, "gini"=MB243$gini, error=MB243$error)


bins.man.wardd2 <- clusterMannhattanOnBins(MB243)

denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),dendroOrder)


# xx <- prcomp(t(MB243Segmented[complete.cases(MB243Segmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(MB243Segmented, clust.rows=denrToPlot, annot_rows=annot_rows)#, column_title = unique(featureData(MB243)$chromosome))
  
```

```{r}

annot_rows = rowAnnotation(ploidy=MB243$ploidy.mod, "obs/exp var"=MB243$observed.variance/MB243$expected.variance, "gini"=MB243$gini, error=MB243$error)


bins.cor.wardd2 <- clusterCorOnBins(MB243)

denrToPlot <- reorder(as.dendrogram(bins.cor.wardd2),dendroOrder)


# xx <- prcomp(t(MB243Segmented[complete.cases(MB243Segmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(MB243Segmented, clust.rows=denrToPlot, annot_rows=annot_rows)
  
```


```{r}
set.seed(42)# set the seed of random number generator 

list.of.packages <- c("HMMcopy", "doParallel", "gtools", "ggplot2")


# ignore all "simple" diagnostic messages (warnings or errors)
suppressMessages(invisible(lapply(list.of.packages, require, character.only = TRUE)))


window_length <- 5e7
min_cnv_changes <- 10

nBootSamples <- 50
min_consec_cnvs <- 5

nthread <- 10
registerDoParallel(nthread)

```


##                       READ IN DATA OF INTEREST
############################################################################
```{r, warning=FALSE, message=FALSE}
## set sample of interest
sample = 'MB243-Nuclei'



## bin size param
bin_kb = 20
bin = bin_kb*1000


# get the readcounts for the bin size of interest
path_cells <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                     sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
path_to_readcounts <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                             sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
files <- list.files(path_to_readcounts, pattern = '.seg', full.names = F)

# set the paths to the reference files
gfile = paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.gc.seg')
mfile =  paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.map.seg')



## Make list of cells
cellList <- list()

names(files) <- sapply(strsplit(files, split = "_|-"), `[[`, 3)

cellList <- foreach(cell = colnames(MB243)) %dopar% {
  print(paste0("Processing cell: ", cell))
  
  
  rfile <- paste(path_cells,files[[cell]],sep = "")
  cellData <- wigsToRangedData(rfile, gfile, mfile)
  cellData
  correctReadcount(cellData)

}
names(cellList) <- colnames(MB243)



```




```{r, warning=FALSE}
library(doParallel)
registerDoParallel(10)
MB243$ploidy.mod[(MB243$ploidy > 3.4 & MB243$ploidy<4)] <- 4
# clonal.cnv.res <- inferClonalCNVs(MB243, cellList, bootstrap = TRUE, nBoot=101)
# saveRDS(clonal.cnv.res.boot, file="mb243_boot_res.rds")
clonal.cnv.res.boot <- readRDS("mb243_boot_res_ploidyfixed.rds")
```


```{r}
for(ploidy in names(clonal.cnv.res.boot)){
  
  for(k in 1:12){
    if(any(sapply(clonal.cnv.res.boot[[ploidy]][[k]], length)>2)){
      pdf(paste0("figures/MB243_", ploidy, "_k_", k, "clones_psuedobulk_ploidyfixed.pdf"), height = 11, width = 8.5)
      print(plotClonalProfilesAtK(clonal.cnv.res.boot[ploidy], k))
      dev.off()      
    }
  }
}



```



Lets plot some GOF metrics for the different k selections:

```{r}


clusterGOFmetrics <- computeGOFMetrics(clonal.cnv.res.boot)

#First ploidy 2:

ploidy2GOF <- sapply(clusterGOFmetrics$Ploidy_2, `[[`, 1)


pdf("figures/MB243ploidy2GOFbyK_ploidyfixed.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()



ploidy3GOF <- sapply(clusterGOFmetrics$Ploidy_3, `[[`, 1)


pdf("figures/MB243ploidy3GOFbyK_ploidyfixed.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy3GOF)), ploidy3GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy3GOF)), ploidy3GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy3GOF)), ploidy3GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy3GOF)), ploidy3GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()



ploidy4GOF <- sapply(clusterGOFmetrics$Ploidy_4, `[[`, 1)


pdf("figures/MB243ploidy4GOFbyK_ploidyfixed.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()


ploidy8GOF <- sapply(clusterGOFmetrics$Ploidy_8, `[[`, 1)


pdf("figures/MB243ploidy8GOFbyK_ploidyfixed.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy4GOF)), ploidy8GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy8GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy8GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy8GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()


```


```{r}

sapply(clonal.cnv.res.boot$Ploidy_4,returnBootstrapFStats)


```
 



```{r}
library(uwot)
library(ggplot2)

my.umap <- umap(dist(t(MB243.ploidy.normed[,-c(1:3), with=F]), method = 'manhattan'))

ploidy <- MB243$ploidy.mod

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Ploidy=factor(ploidy))

ggplot(toPlot, aes(UMAP1, UMAP2, col = Ploidy)) +
  geom_point()


```


```{r}

my.mds <- cmdscale(dist(t(MB243.ploidy.normed[, -c(1:3), with = F]), method = "manhattan"))


toPlot <- data.frame(MDS1 = my.mds[, 1], MDS2 = my.mds[, 2], Ploidy = factor(ploidy))



ggplot(toPlot, aes(MDS1, MDS2, col = Ploidy)) +
  geom_point()


```

Based on the plots above an manually examining the cells going into the ploidy 2 clone, it seems that its made up of 3 normal cells and 2 tumour cells. Combining them 
into a single clone does not make sense, and the 2 tumour cells is to few to form a clone of their own. Therefore, I would tend to 


```{r}


clonalCNVProfiles <- clonal.cnv.res.boot$Ploidy_3$k_1$Cluster_1$pseudobulk[,c(1,2,3), with=FALSE]


# ploidy2clones <- round(2^(clonal.cnv.res.boot$Ploidy_2$k_1$Cluster_1$hmmres$mus[,1]+1)[clonal.cnv.res.boot$Ploidy_2$k_1$Cluster_1$hmmres$state])
ploidy3clones <- round((2^(clonal.cnv.res.boot$Ploidy_3$k_1$Cluster_1$hmmres$mus[,1])*3)[clonal.cnv.res.boot$Ploidy_3$k_1$Cluster_1$hmmres$state])

ploidy4clones <- lapply(clonal.cnv.res.boot$Ploidy_4$k_8, function(k.res){
  return(round(2^(k.res$hmmres$mus[,1]+2)[k.res$hmmres$state]))
})

ploidy4clones <- do.call(cbind,ploidy4clones[as.logical(sapply(ploidy4clones, length))])
  
clonalCNVProfiles <- cbind(clonalCNVProfiles, ploidy3clones, ploidy4clones )

colnames(clonalCNVProfiles)[-c(1:3)] <- paste0("Clone_", 1:4) 

```



```{r}

saveRDS(clonalCNVProfiles, file = "~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/MB243_draft3_clonal_cnv.rds")
png("~/mb243_clonal3_cnv_draft.png", width=10, height=5, unit="in", res=600)
print(plotComplexHeatmapCommonSegs(clonalCNVProfiles, clust.rows = FALSE, column_title = unique(clonalCNVProfiles$chr)))
dev.off()
```


Now we need to save the per-cell corrected read counts with a table assigning them to clones. First lets create the clone assignment table:



```{r}

ploidy3cloneCells <-clonal.cnv.res.boot$Ploidy_3$k_1$Cluster_1['cells']

ploidy4clonesCells <- lapply(clonal.cnv.res.boot$Ploidy_4$k_8, function(x) return(x['cells']))

ploidy4clonesCells <- ploidy4clonesCells[sapply(ploidy4clonesCells, function(x) length(x[[1]]))>=5]

allCloneCells <- c(list(ploidy3cloneCells),ploidy4clonesCells)

names(allCloneCells) <- paste0("Clone_", 1:4) 



cloneAssignment <- rbindlist(allCloneCells, idcol = "Clone")

notAssignedCells <- data.frame(Clone = "Not Assigned", cells=colnames(MB243)[!colnames(MB243)%in%cloneAssignment$cells])

cloneAssignment <- rbind(cloneAssignment, notAssignedCells)

write.csv(cloneAssignment, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/MB243_cell_clone_assignments.csv")

```



Now lets write out the HMMCopy matrix


```{r}


names(cellList)

HMMCopyMat <- sapply(cellList, `[[`, "copy")

HMMCopyMat <- cbind(cellList[[1]][,c(1:3)], HMMCopyMat)

write.csv(HMMCopyMat, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/MB243_hmmcopy_20kb_logR.csv")

```


Now the scAbsolute:



```{r}
library(dplyr)
gccor <- estimate_gc_correction(MB243)

scAbsoluteRC <- assayDataElement(MB243,"calls")*1/gccor

write.csv(scAbsoluteRC, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/MB243_scAbsolute_500kb_corReadCount.csv")

scAbsoluteTCN <- assayDataElement(MB243,"copynumber")
write.csv(scAbsoluteTCN, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/MB243_hmmcopy_500kb_TCN.csv")

```



