---
title: "Test calling clonal cnvs in STPPDX"
output:
  html_document:
    df_print: paged
---
  Here, we look at the results of running scAbsolute on this sample.


```{r}
library(ComplexHeatmap)
library(data.table)
library(QDNAseq)
library(RColorBrewer)
library(dplyr)


source("~/scAbsolute-main/R/visualization.R")
source("~/scAbsolute-main/R/mean-variance.R")
source("~/scAbsolute-main/R/scAbsolute.R")
source("~/scAbsolute-main/R/core.R")



source("~/MB_SCSEQ/Figure01/CloneInference/commonSegmentation.R")
source("~/MB_SCSEQ/Figure01/CloneInference/plotFunctionsCNV.R")
source("~/MB_SCSEQ/Figure01/CloneInference/inferClonalCNVProfiles.R")
source("~/MB_SCSEQ/Figure01/CloneInference/calculateBootstrappedStatistics.R")

```

## 10x data

Load in the results for all the STP samples here:
  
```{r}


STPNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STP-Nuclei-2/1000/predict/out.rds")
protocolData(STPNucres) <- AnnotatedDataFrame()
colnames(STPNucres) <- gsub(colnames(STPNucres), pat = "\\-[0-9]\\.filtered\\.sorted$", rep = "")


# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPR-Nuclei//500/predict/out.rds")

# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/RCMB18-PDX/500/predict/out.rds")


# STPPDXres <- STPPDXres[,STPPDXres$ploidy.mod %in% seq(1,4)]
# STPRPDXres <- STPRPDXres[,STPRPDXres$ploidy.mod %in% seq(1,4)]
# STPNucres <- STPNucres[,STPNucres$ploidy.mod %in% seq(1,4)]
# STPRNucres <- STPRNucres[,STPRNucres$ploidy.mod %in% seq(1,4)]

```

## STP Nuc clone identification

```{r}
out.dir <- "~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsoluteFigures/qc/STPNuc"
dir.create(out.dir, recursive = TRUE)

pdf(file.path(out.dir, "variance_filter_hist.pdf"), height = 4, width = 4)
hist(STPNucres$observed.variance/STPNucres$expected.variance, breaks = 50, xlab="Observed/Expected Variance", main="")
abline(v=mad(STPNucres$observed.variance/STPNucres$expected.variance)*2+median(STPNucres$observed.variance/STPNucres$expected.variance))
dev.off()
```

There are clear outliers based on variance, which we remove.

```{r}

pdf(file.path(out.dir, "gini_filter_hist.pdf"), height = 4, width = 4)
hist(STPNucres$gini_normalized, breaks = 50, xlab="Normalized Gini", main="")
abline(v=mad(STPNucres$gini_normalized)*2+median(STPNucres$gini_normalized))
dev.off()

```

```{r}

hist(STPNucres$error, breaks = 60)
abline(v=mad(STPNucres$error)*2+median(STPNucres$error))


```

Plotting some cells for Supplementary Figure on QC:

```{r}

pdf("misc/STPNuclei_ploidy4_AACTCCCAGAGTAATC.pdf", width=7, height=4)
plotCopynumber(STPNucres[,"AACTCCCAGAGTAATC"], main="", 
               showMarker = FALSE, 
               readinfo = FALSE,
               ylim=c(0,14))
dev.off()


```



We plot a comparison of the noisy and not noisy cells for the supplemental figures. 

```{r}

pdf(file.path(out.dir, "heatmap_all_cells.pdf"), height=.35*ncol(STPNucres)/25.4, width=160/25.4) ## mm to inch
plotComplexHeatmapChromosomes(QDNAobject = STPNucres, background = "transparent")
dev.off()

```


## Run filters
```{r}
var.filter <- mad(STPNucres$observed.variance / STPNucres$expected.variance) * 2 + median(STPNucres$observed.variance / STPNucres$expected.variance) > STPNucres$observed.variance / STPNucres$expected.variance
gini.filter <- mad(STPNucres$gini_normalized) * 2 + median(STPNucres$gini_normalized) > STPNucres$gini_normalized
# error.filter <- mad(STPNucres$error)*2+median(STPNucres$error) > STPNucres$error
## Ploidy 0 doesn't work for ploidy normalization
ploidy.filter <- STPNucres$ploidy.mod > 0
filtered_out_cells <- STPNucres[, !(var.filter & gini.filter & ploidy.filter)]

STPNucres <- STPNucres[, var.filter & gini.filter & ploidy.filter]


```


```{r}

pdf(file.path(out.dir, "heatmap_noisy_cells.pdf"), height=3.5*ncol(filtered_out_cells)/25.4, width=160/25.4)
plotComplexHeatmapChromosomes(QDNAobject = filtered_out_cells, background = "transparent")
dev.off()

pdf(file.path(out.dir, "heatmap_clean_cells.pdf"), height=.35*ncol(STPNucres)/25.4, width=160/25.4)
plotComplexHeatmapChromosomes(QDNAobject = STPNucres, background = "transparent")
dev.off()

```



Note, these results were already filtered once, as I looked through the good cells only for fixing the mis-identified ploidy.

```{r}
STPNucSegmented <- mapCellsToCommonBreakpoints(STPNucres, mergeWidth = 2)

ploidy.data <- data.frame(chr="ploidy", "start"=-1, end=-1)
ploidy.data <- cbind(ploidy.data, t(data.frame(STPNucres$ploidy.mod)))

STPNuc.ploidy.normed <- copy(STPNucSegmented)

for(cell in colnames(STPNucres)){
  
  STPNuc.ploidy.normed[,(cell):= STPNuc.ploidy.normed[,cell, with=F]/ STPNucres[,cell]$ploidy.mod*2]
}

STPNuc.ploidy.normed <- rbind(STPNuc.ploidy.normed, ploidy.data, use.names=F)


```

```{r}
dendroOrder <- rowSums(abs(t(assayDataElement(STPNucres, "copynumber"))-STPNucres$ploidy.mod), na.rm = TRUE)

STPNucres$TECHNOLOGY <- '1'


replicating <- predict_replicating(pData(STPNucres), batch = 'technology')$replicating

annot_rows = rowAnnotation(replicating = replicating)


segment.man.wardd2 <- hclust(dist(t(STPNucSegmented[,c(-1,-2,-3)]), method="manhattan"), method = "ward.D2")
denrToPlot <- reorder(as.dendrogram(segment.man.wardd2),dendroOrder)


plotComplexHeatmapCommonSegs(STPNucSegmented, clust.rows=segment.man.wardd2, column_title = unique(STPNucSegmented$chr), annot_rows=annot_rows)

```



```{r}

annot_rows = rowAnnotation(ploidy=STPNucres$ploidy.mod, "obs/exp var"=STPNucres$observed.variance/STPNucres$expected.variance, "gini"=STPNucres$gini, error=STPNucres$error)


bins.man.wardd2 <- clusterMannhattanOnBins(STPNucres)

denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),dendroOrder)


# xx <- prcomp(t(STPNucSegmented[complete.cases(STPNucSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(STPNucSegmented, clust.rows=denrToPlot, column_title = unique(STPNucSegmented$chr))#, annot_rows=annot_rows)

```

```{r}

annot_rows = rowAnnotation(ploidy=STPNucres$ploidy.mod, "obs/exp var"=STPNucres$observed.variance/STPNucres$expected.variance, "gini"=STPNucres$gini, error=STPNucres$error)


bins.cor.wardd2 <- clusterCorOnBins(STPNucres)

denrToPlot <- reorder(as.dendrogram(bins.cor.wardd2),dendroOrder)


# xx <- prcomp(t(STPNucSegmented[complete.cases(STPNucSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(STPNucSegmented, clust.rows=denrToPlot, column_title = unique(featureData(STPNucres)$chromosome))

```


Lets plot all the cell results for manual review:
  
```{r}

plotDataset(STPNucres, file="STPNuc2_1MB_scAbs_allcells.pdf", f=plotCopynumber, correction=TRUE)

```



```{r}
set.seed(42)# set the seed of random number generator 

list.of.packages <- c("HMMcopy", "doParallel", "gtools", "ggplot2")


# ignore all "simple" diagnostic messages (warnings or errors)
suppressMessages(invisible(lapply(list.of.packages, require, character.only = TRUE)))


window_length <- 5e7
min_cnv_changes <- 10

nBootSamples <- 50
min_consec_cnvs <- 5

nthread <- 10
registerDoParallel(nthread)

```


##                       READ IN DATA OF INTEREST
############################################################################
```{r, warning=FALSE, message=FALSE}
## set sample of interest
sample = 'STP-Nuclei'



## bin size param
bin_kb = 20
bin = bin_kb*1000





# get the readcounts for the bin size of interest
path_cells <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                     sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
path_to_readcounts <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                             sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
files <- list.files(path_to_readcounts, pattern = '.seg', full.names = F)

# set the paths to the reference files
gfile = paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.gc.seg')
mfile =  paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.map.seg')



## Make list of cells
cellList <- list()

names(files) <- sapply(strsplit(files, split = "_|-"), `[[`, 3)

cellList <- foreach(cell = colnames(STPNucres)) %dopar% {
  print(paste0("Processing cell: ", cell))
  
  
  rfile <- paste(path_cells,files[[cell]],sep = "")
  cellData <- wigsToRangedData(rfile, gfile, mfile)
  
  correctReadcount2(cellData)
  
}
names(cellList) <- colnames(STPNucres)



```


```{r}
# 
# registerDoParallel(8)
# # 
# clonal.cnv.res.boot <- inferClonalCNVs(STPNucres, cellList, bootstrap = TRUE, nBoot=101)
# saveRDS(clonal.cnv.res.boot, file="STPNuc2_boot_res.rds")
clonal.cnv.res.boot <- readRDS("/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STPNuc2_1MB_boot_res.rds")
```


```{r}

for(ploidy in names(clonal.cnv.res.boot)){
  
  for(k in 1:12){
    pdf(paste0("STPNuc2_",ploidy,"_k_", k, "clones_psuedobulk.pdf"), height = 11, width = 8.5)
    print(plotClonalProfilesAtK(clonal.cnv.res.boot[ploidy], k))
    dev.off()
  }
  
}



```


Lets plot some GOF metrics for the different k selections:
  
```{r}


clusterGOFmetrics <- computeGOFMetrics(clonal.cnv.res.boot)

#First ploidy 2:

ploidy2GOF <- sapply(clusterGOFmetrics$Ploidy_2, `[[`, 1)


pdf("STPNuc2_1MB_ploidy2GOFbyK.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy2GOF)), ploidy2GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()


#Now ploidy 4:

ploidy4GOF <- sapply(clusterGOFmetrics$Ploidy_4, `[[`, 1)


pdf("STPNuc2_1MB_ploidy4GOFbyK.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()

```


```{r}
sapply(clonal.cnv.res.boot$Ploidy_4,returnBootstrapFStats)
```



There doesn't seem to be any local optima in the F statstitics. We can take a look at the GOF metrics, where 2-5 seem equal

The number of clones per K is:

```{r}
sapply(clonal.cnv.res.boot$Ploidy_4, function(x) sum(sapply(x, function(y) length(y$cells)>=5)))

```

I think in this case, it makes sense to investigate K=5, K=7, and K=10.


```{r}
library(uwot)
library(ggplot2)

my.umap <- umap(dist(t(STPNucSegmented[,-c(1:3), with=F])[STPNucres$ploidy.mod==4,], method = 'manhattan'))

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_5, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```


```{r}


cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_7, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```



```{r}


cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_10, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```

```{r}
cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_5, `[`, "cells"), idcol="Cluster")

my.mds <- cmdscale(dist(t(STPNucSegmented[,-c(1:3), with=F])[STPNucres$ploidy.mod==4,], method='manhattan'))


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```

```{r}

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_7, `[`, "cells"), idcol="Cluster")


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```

```{r}

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_10, `[`, "cells"), idcol="Cluster")


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```




```{r}
library(uwot)
library(ggplot2)

my.umap <- umap(dist(t(STPNucSegmented[,-c(1:3), with=F])[STPNucres$ploidy.mod==2,], method = 'manhattan'))

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_2$k_6, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```


After examining the singlecell profiles, and the clonal profiles, I think seems to me that k=10 may be optimal for the tetraploid cells.
There seems to be a major clone, then a originating from there with gain of 7, and a seperate clone with CT on 14 split into a gain of 7 and no gain of 7.
Alternatively, it may be that the major clone is actually a child of the non-CT 14 branch which lost 7. 

For the ploidy 2 state, we only have the normal cells, which by AIC/BIC most closely resemble a single clone at k=4.

```{r}

clonalCNVProfiles <- clonal.cnv.res.boot$Ploidy_4$k_1$Cluster_1$pseudobulk[,c(1,2,3), with=FALSE]

ploidy4clones <- lapply(clonal.cnv.res.boot$Ploidy_4$k_10, function(k.res){
  return(round(2^(k.res$hmmres$mus[,1]+2)[k.res$hmmres$state]))
})


ploidy2clones <- lapply(clonal.cnv.res.boot$Ploidy_2$k_4, function(k.res){
  return(round(2^(k.res$hmmres$mus[,1]+1)[k.res$hmmres$state]))
})

ploidy4clones <- do.call(cbind,ploidy4clones[as.logical(sapply(ploidy4clones, length))])
ploidy2clones <- do.call(cbind,ploidy2clones[as.logical(sapply(ploidy2clones, length))])
  
clonalCNVProfiles <- cbind(clonalCNVProfiles, ploidy4clones,ploidy2clones )

colnames(clonalCNVProfiles)[-c(1:3)] <- c(paste0("Clone_", 1:4),"Diploid")

```



```{r}

saveRDS(clonalCNVProfiles, file="~/STPNucres_1MB_draft2_clonal_cnv.rds")
png("~/STPNucres_1MB_clonal_cnv_draft.png", width=10, height=5, unit="in", res=1000)
plotComplexHeatmapCommonSegs(clonalCNVProfiles, clust.rows = FALSE, column_title = unique(clonalCNVProfiles$chr))
dev.off()
```




```{r}


ploidy4clonesCells <- lapply(clonal.cnv.res.boot$Ploidy_4$k_10, function(x) return(x['cells']))
ploidy4clonesCells <- ploidy4clonesCells[sapply(ploidy4clonesCells, function(x) length(x[[1]]))>=5]

ploidy2cloneCells <- lapply(clonal.cnv.res.boot$Ploidy_2$k_4, function(x) return(x['cells']))
ploidy2cloneCells <- ploidy2cloneCells[sapply(ploidy2cloneCells, function(x) length(x[[1]]))>=5]


allCloneCells <- c(ploidy4clonesCells,ploidy2cloneCells)

names(allCloneCells) <- c(paste0("Clone_", 1:4),"Diploid")



cloneAssignment <- rbindlist(allCloneCells, idcol = "Clone")

notAssignedCells <- data.frame(Clone = "Not Assigned", cells=colnames(STPNucres)[!colnames(STPNucres)%in%cloneAssignment$cells])

cloneAssignment <- rbind(cloneAssignment, notAssignedCells)

write.csv(cloneAssignment, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_Nuclei_cell_clone_assignments.csv")

```



```{r}

HMMCopyMat <- sapply(cellList, `[[`, "copy")

HMMCopyMat <- cbind(cellList[[1]][,c(1:3)], HMMCopyMat)

write.csv(HMMCopyMat, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_Nuclei_hmmcopy_20kb_logR.csv")


```



```{r}
library(dplyr)

gccor <- estimate_gc_correction(STPNucres)

scAbsoluteRC <- assayDataElement(STPNucres,"calls")*1/gccor

write.csv(scAbsoluteRC, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_Nuclei_scAbsolute_500kb_corReadCount.csv")

scAbsoluteTCN <- assayDataElement(STPNucres, "copynumber")
write.csv(scAbsoluteTCN, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_Nuclei_scAbs_500kb_TCN.csv")

```


