---
title: "Test calling clonal cnvs in STP-PDX"
output:
  html_document:
    df_print: paged
---
Here, we look at the results of running scAbsolute on this sample.


```{r}
library(ComplexHeatmap)
library(data.table)
library(QDNAseq)
library(RColorBrewer)
library(HMMcopy)
library(doParallel)
library(gtools)
library(ggplot2)


source("~/scAbsolute-main/R/visualization.R")
source("~/scAbsolute-main/R/mean-variance.R")
source("~/scAbsolute-main/R/scAbsolute.R")
source("~/scAbsolute-main/R/core.R")



source("~/MB_SCSEQ/Figure01/CloneInference/commonSegmentation.R")
source("~/MB_SCSEQ/Figure01/CloneInference/plotFunctionsCNV.R")
source("~/MB_SCSEQ/Figure01/CloneInference/inferClonalCNVProfiles.R")
source("~/MB_SCSEQ/Figure01/CloneInference/calculateBootstrappedStatistics.R")
```

## 10x data

Load in the results for all the STP samples here:

```{r}

STPPDX <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STP-PDX/500/predict/out.rds")
# STPRPDXres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPR-PDX/500/predict/out.rds")
# STPPDX <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPPDX-Nuclei/500/predict/out.rds")
protocolData(STPPDX) <- AnnotatedDataFrame()
colnames(STPPDX) <- gsub(colnames(STPPDX), pat = "\\-[0-9]\\.filtered\\.sorted$", rep = "")

# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/STPR-Nuclei//500/predict/out.rds")

# STPRNucres <- readRDS("~/groups/OE0585/internal/p163v/scAbsoluteWorkflow/results/scale/RCMB18-PDX/500/predict/out.rds")


# STPPDXres <- STPPDXres[,STPPDXres$ploidy.mod %in% seq(1,4)]
# STPRPDXres <- STPRPDXres[,STPRPDXres$ploidy.mod %in% seq(1,4)]
# STPPDX <- STPPDX[,STPPDX$ploidy.mod %in% seq(1,4)]
# STPRNucres <- STPRNucres[,STPRNucres$ploidy.mod %in% seq(1,4)]

```

## STPPDX clone identification

```{r}


out.dir <- "~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsoluteFigures/qc/STPPDX"
dir.create(out.dir, recursive = TRUE)

pdf(file.path(out.dir, "variance_filter_hist.pdf"), height = 4, width = 4)
hist(STPPDX$observed.variance/STPPDX$expected.variance, breaks = 50, xlab="Observed/Expected Variance", main="")
abline(v=mad(STPPDX$observed.variance/STPPDX$expected.variance)*2+median(STPPDX$observed.variance/STPPDX$expected.variance))
dev.off()

hist(STPPDX$observed.variance/STPPDX$expected.variance, breaks = 50)
abline(v=mad(STPPDX$observed.variance/STPPDX$expected.variance)*2+median(STPPDX$observed.variance/STPPDX$expected.variance))
```

There are clear outliers based on variance, which we remove.

```{r}



pdf(file.path(out.dir, "gini_filter_hist.pdf"), height = 4, width = 4)
hist(STPPDX$gini_normalized, breaks = 50, xlab="Normalized Gini", main="")
abline(v=mad(STPPDX$gini_normalized)*2+median(STPPDX$gini_normalized))
dev.off()

hist(STPPDX$gini_normalized, breaks = 50)
abline(v=mad(STPPDX$gini_normalized)*2+median(STPPDX$gini_normalized))

```

```{r}

hist(STPPDX$error, breaks = 60)
abline(v=mad(STPPDX$error)*2+median(STPPDX$error))

```


We plot a comparison of the noisy and not noisy cells for the supplemental figures. 

```{r}

pdf(file.path(out.dir, "heatmap_all_cells.pdf"), height=.35*ncol(STPPDX)/25.4, width=160/25.4) ## mm to inch
plotComplexHeatmapChromosomes(QDNAobject = STPPDX, background = "transparent")
dev.off()

print(ncol(STPPDX))

```


## Run filters
```{r}
var.filter <- mad(STPPDX$observed.variance / STPPDX$expected.variance) * 2 + median(STPPDX$observed.variance / STPPDX$expected.variance) > STPPDX$observed.variance / STPPDX$expected.variance
gini.filter <- mad(STPPDX$gini_normalized) * 2 + median(STPPDX$gini_normalized) > STPPDX$gini_normalized
# error.filter <- mad(STPPDX$error)*2+median(STPPDX$error) > STPPDX$error
## Ploidy 0 doesn't work for ploidy normalization
ploidy.filter <- STPPDX$ploidy.mod > 0
filtered_out_cells <- STPPDX[, !(var.filter & gini.filter & ploidy.filter)]

STPPDX <- STPPDX[, var.filter & gini.filter & ploidy.filter]

print(ncol(STPPDX))
print(ncol(filtered_out_cells))


```


```{r}

pdf(file.path(out.dir, "heatmap_noisy_cells.pdf"), height=3.5*ncol(filtered_out_cells)/25.4, width=160/25.4)
plotComplexHeatmapChromosomes(QDNAobject = filtered_out_cells, background = "transparent")
dev.off()

pdf(file.path(out.dir, "heatmap_clean_cells.pdf"), height=.35*ncol(STPPDX)/25.4, width=160/25.4)
plotComplexHeatmapChromosomes(QDNAobject = STPPDX, background = "transparent")
dev.off()

```



```{r}
# 
# var.filter <- mad(STPPDX$observed.variance/STPPDX$expected.variance)*2+median(STPPDX$observed.variance/STPPDX$expected.variance) > STPPDX$observed.variance/STPPDX$expected.variance
# gini.filter <- mad(STPPDX$gini_normalized)*2+median(STPPDX$gini_normalized) > STPPDX$gini_normalized
# # error.filter <- mad(STPPDX$error)*2+median(STPPDX$error) > STPPDX$error
# ## Ploidy 0 doesn't work for ploidy normalization
# ploidy.filter <- STPPDX$ploidy.mod > 0
# STPPDX <- STPPDX[,var.filter&gini.filter&ploidy.filter]

```


Lets plot all the cell results for manual review:

```{r}

plotDataset(STPPDX, file="STPPDX_scAbs_allcells.pdf", f=plotCopynumber)

```


```{r}
STPPDXSegmented <- mapCellsToCommonBreakpoints(STPPDX, mergeWidth = 2)

ploidy.data <- data.frame(chr="ploidy", "start"=-1, end=-1)
ploidy.data <- cbind(ploidy.data, t(data.frame(STPPDX$ploidy.mod)))

STPPDX.ploidy.normed <- copy(STPPDXSegmented)

for(cell in colnames(STPPDX)){
  
  STPPDX.ploidy.normed[,(cell):= STPPDX.ploidy.normed[,cell, with=F]/ STPPDX[,cell]$ploidy.mod*2]
}

STPPDX.ploidy.normed <- rbind(STPPDX.ploidy.normed, ploidy.data, use.names=F)


```

```{r}
dendroOrder <- rowSums(abs(t(assayDataElement(STPPDX, "copynumber"))-STPPDX$ploidy.mod), na.rm = TRUE)

annot_rows = rowAnnotation(ploidy=STPPDX$ploidy.mod, "obs/exp var"=STPPDX$observed.variance/STPPDX$expected.variance, "gini"=STPPDX$gini, error=STPPDX$error)


ploidy.normed.man.wardd2 <- hclust(dist(t(STPPDX.ploidy.normed[,c(-1,-2,-3)]), method="manhattan"), method = "ward.D2")

  
plotComplexHeatmapCommonSegs(STPPDXSegmented, clust.rows=ploidy.normed.man.wardd2, annot_rows=annot_rows)
  
```

```{r}

annot_rows = rowAnnotation(ploidy=STPPDX$ploidy.mod, "obs/exp var"=STPPDX$observed.variance/STPPDX$expected.variance, "gini"=STPPDX$gini, error=STPPDX$error)


bins.man.wardd2 <- clusterMannhattanOnBins(STPPDX)

denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),dendroOrder)


# xx <- prcomp(t(STPPDXSegmented[complete.cases(STPPDXSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(STPPDXSegmented, clust.rows=denrToPlot, annot_rows=annot_rows)#, column_title = unique(featureData(STPPDX)$chromosome))
  
```

```{r}

annot_rows = rowAnnotation(ploidy=STPPDX$ploidy.mod, "obs/exp var"=STPPDX$observed.variance/STPPDX$expected.variance, "gini"=STPPDX$gini, error=STPPDX$error)


bins.cor.wardd2 <- clusterCorOnBins(STPPDX)

denrToPlot <- reorder(as.dendrogram(bins.cor.wardd2),dendroOrder)


# xx <- prcomp(t(STPPDXSegmented[complete.cases(STPPDXSegmented),c(-1,-2,-3), with=FALSE]))$x[,"PC1"]
# denrToPlot <- reorder(as.dendrogram(bins.man.wardd2),xx)

plotComplexHeatmapCommonSegs(STPPDXSegmented, clust.rows=denrToPlot, annot_rows=annot_rows)
  
```


```{r}
set.seed(42)# set the seed of random number generator 

list.of.packages <- c("HMMcopy", "doParallel", "gtools", "ggplot2")


# ignore all "simple" diagnostic messages (warnings or errors)
suppressMessages(invisible(lapply(list.of.packages, require, character.only = TRUE)))


window_length <- 5e7
min_cnv_changes <- 10

nBootSamples <- 50
min_consec_cnvs <- 5

nthread <- 10
registerDoParallel(nthread)

```


##                       READ IN DATA OF INTEREST
############################################################################
```{r, warning=FALSE, message=FALSE}
## set sample of interest
sample = 'STP-PDX'



## bin size param
bin_kb = 20
bin = bin_kb*1000





# get the readcounts for the bin size of interest
path_cells <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                     sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
path_to_readcounts <- paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/all_samples/', 
                             sample,'/readCount_filtered_bam/bin_', bin_kb,'kb/')
files <- list.files(path_to_readcounts, pattern = '.seg', full.names = F)

# set the paths to the reference files
gfile = paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.gc.seg')
mfile =  paste0('/omics/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/HMMcopy_10x_scDNA/refdata/bin_', bin_kb, 'kb/hg19.', bin_kb, 'kb.map.seg')



## Make list of cells
cellList <- list()

names(files) <- sapply(strsplit(files, split = "_|-"), `[[`, 3)

cellList <- foreach(cell = colnames(STPPDX)) %dopar% {
  print(paste0("Processing cell: ", cell))
  
  
  rfile <- paste(path_cells,files[[cell]],sep = "")
  cellData <- wigsToRangedData(rfile, gfile, mfile)
  
  correctReadcount2(cellData)

}
names(cellList) <- colnames(STPPDX)



```


```{r}
library(doParallel)
registerDoParallel(10)
# 
# clonal.cnv.res.boot <- inferClonalCNVs(STPPDX, cellList, bootstrap = TRUE, nBoot=101)
# saveRDS(clonal.cnv.res.boot, file="STP-PDX_boot_res.rds")
clonal.cnv.res.boot <- readRDS('STP-PDX_boot_res.rds')
```


```{r}
for(ploidy in names(clonal.cnv.res.boot)){
  
  for(k in 1:12){
    pdf(paste0("STPPDX_",ploidy,"_k_", k, "clones_psuedobulk.pdf"), height = 11, width = 8.5)
    print(plotClonalProfilesAtK(clonal.cnv.res.boot[ploidy], k))
    dev.off()
  }
  
}



```



Lets plot some GOF metrics for the different k selections:

```{r}


clusterGOFmetrics <- computeGOFMetrics(clonal.cnv.res.boot)

ploidy4GOF <- sapply(clusterGOFmetrics$Ploidy_4, `[[`, 1)


pdf("STPPDXploidy4GOFbyK.pdf", onefile = TRUE)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["RMSE",], xlab="K", ylab="RMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["logRMSE",], xlab="K", ylab="logRMSE", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["AIC",], xlab="K", ylab="AIC", type = "b", pch=16)
plot(seq_len(ncol(ploidy4GOF)), ploidy4GOF["BIC",], xlab="K", ylab="BIC", type = "b", pch=16)
dev.off()

```


```{r}
sapply(clonal.cnv.res.boot$Ploidy_4,returnBootstrapFStats)

```
Here, k=5 and k=11 both look like local optima. Lets visualize whats going on:



```{r}
library(uwot)
library(ggplot2)

my.umap <- umap(dist(t(STPPDXSegmented[,-c(1:3), with=F])[STPPDX$ploidy.mod==4,]))

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_5, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```


```{r}


cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_11, `[`, "cells"), idcol="Cluster")

toPlot <- data.frame(UMAP1 = my.umap[,1], UMAP2=my.umap[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.umap), cluster_assignment$cells)])

ggplot(toPlot, aes(UMAP1, UMAP2, col=Cluster)) + geom_point()


```

```{r}
cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_5, `[`, "cells"), idcol="Cluster")

my.mds <- cmdscale(dist(t(STPPDXSegmented[,-c(1:3), with=F])[STPPDX$ploidy.mod==4,]))


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```

```{r}

cluster_assignment <- rbindlist(lapply(clonal.cnv.res.boot$Ploidy_4$k_5, `[`, "cells"), idcol="Cluster")


toPlot <- data.frame(MDS1 = my.mds[,1], MDS2=my.mds[,2], Cluster=cluster_assignment$Cluster[match(rownames(my.mds), cluster_assignment$cells)])



ggplot(toPlot, aes(MDS1, MDS2, col=Cluster)) + geom_point()

```


The k=5 case seems more reasonable here, so we will go with it. 



```{r}

clonalCNVProfiles <- clonal.cnv.res.boot$Ploidy_4$k_1$Cluster_1$pseudobulk[,c(1,2,3), with=FALSE]

ploidy4clones <- lapply(clonal.cnv.res.boot$Ploidy_4$k_5, function(k.res){
  return(round(2^(k.res$hmmres$mus[,1]+2)[k.res$hmmres$state]))
})

ploidy4clones <- do.call(cbind,ploidy4clones[as.logical(sapply(ploidy4clones, length))])
  
clonalCNVProfiles <- cbind(clonalCNVProfiles, ploidy4clones )

colnames(clonalCNVProfiles)[-c(1:3)] <- paste0("Clone_", 1:5) 

```



```{r}

saveRDS(clonalCNVProfiles, file="~/STPPDX_draft_clonal_cnv.rds")
png("~/stp_pdx_clonal_cnv_draft.png", width=10, height=5, unit="in", res=1000)
plotComplexHeatmapCommonSegs(clonalCNVProfiles, clust.rows = FALSE, column_title = unique(clonalCNVProfiles$chr))
dev.off()
```


```{r}


ploidy4clonesCells <- lapply(clonal.cnv.res.boot$Ploidy_4$k_5, function(x) return(x['cells']))

ploidy4clonesCells <- ploidy4clonesCells[sapply(ploidy4clonesCells, function(x) length(x[[1]]))>=5]

allCloneCells <- ploidy4clonesCells

names(allCloneCells) <- paste0("Clone_", 1:5) 



cloneAssignment <- rbindlist(allCloneCells, idcol = "Clone")

if(any(!colnames(STPPDX)%in%cloneAssignment$cells)){
  notAssignedCells <- data.frame(Clone = "Not Assigned", cells=colnames(STPPDX)[!colnames(STPPDX)%in%cloneAssignment$cells])
  cloneAssignment <- rbind(cloneAssignment, notAssignedCells)
}



write.csv(cloneAssignment, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_PDX_cell_clone_assignments.csv")

```



```{r}

HMMCopyMat <- sapply(cellList, `[[`, "copy")

HMMCopyMat <- cbind(cellList[[1]][,c(1:3)], HMMCopyMat)

write.csv(HMMCopyMat, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_PDX_hmmcopy_20kb_logR.csv")


```


```{r}
library(dplyr)


gccor <- estimate_gc_correction(STPPDX)

scAbsoluteRC <- assayDataElement(STPPDX,"calls")*1/gccor

write.csv(scAbsoluteRC, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_PDX_scAbsolute_500kb_corReadCount.csv")


scAbsoluteTCN <- assayDataElement(STPPDX,"copynumber")
write.csv(scAbsoluteTCN, file="~/groups/OE0540/internal/projects/chromothripsis_medulloblastoma/scAbsolute_clones/STP_PDX_hmmcopy_500kb_TCN.csv")

```


